Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-22 manuscript/HIAs.qmd
methods map no country

temp |>
ggplot(aes(
    x = infrastructureIndex,
    y = n,
    fill = condition
  )) +
  geom_bar(
    position = "fill",
    stat = "identity"
  ) +
  geom_text(aes(label = lab),
    position = position_fill(vjust = 0.5),
    color= "black", vjust = 0.5, size = 4) +
  theme_minimal(base_size = 15) +
  theme(
    panel.grid = element_blank(), 
    axis.text.x = element_text(margin = margin(t = -10)),
    axis.text.y = element_blank(),
    strip.text = element_textbox(
      size = 12,
      halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3))) +
  guides(fill = guide_legend("Indicator values")) +
  ylab("Fraction of data points") +
  xlab("Human Impact Areas") +
  scale_fill_manual(values = c("#E85437","#FBBF00", "#B5DF73", "#009000")) +
  facet_grid(~indicator)

@@

# Infratructure in each municipality
infraMuniMap <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human Impact\nArea Class"
  ) +
  tm_shape(muni3) +
  tm_borders(lwd = 3, col = "black") +
  tm_facets(by = "Municipality") +
  tm_layout(
    legend.show = FALSE,
    panel.label.height = 0)

# A figure with just the legend
infraMuniMap_l <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human\nImpact\nArea"
  ) +
  tm_layout(legend.only = TRUE,
            legend.position = c("left", "bottom"),
            legend.outside = TRUE)

@@

(methodsMap <- tmap_arrange(
  positionMap,
  muniPlot,
  infraMuniMap_l,
  infraMuniMap,
  widths = c(.35, .65),
  heights = c(.6, .4),
  outer.margins = .01
))

>>>>

temp |>
ggplot(aes(
    x = infrastructureIndex,
    y = n,
    fill = condition
  )) +
  geom_bar(
    position = "fill",
    stat = "identity"
  ) +
  geom_text(aes(label = lab),
    position = position_fill(vjust = 0.5),
    color= "black", vjust = 0.5, size = 4) +
  theme_minimal(base_size = 15) +
  theme(
    panel.grid = element_blank(), 
    axis.text.x = element_text(margin = margin(t = -10)),
    axis.text.y = element_blank(),
    strip.text = element_textbox(
      size = 12,
      halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3))) +
  guides(fill = guide_legend("Indicator values")) +
  ylab("Fraction of data points") +
  xlab("Human Impact Areas") +
  scale_fill_manual(values = c("#E85437","#FBAF00", "#B5DF73", "#009000")) +
  facet_grid(~indicator)

@@

# Infratructure in each municipality
(infraMuniMap <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human Impact Areas"
  ) +
  tm_layout(
    legend.show = F,
    panel.label.height = 0) +
  tm_shape(muni3) +
  tm_borders(lwd = 3, col = "black") +
  tm_facets(by = "Municipality"))

# A figure with just the legend
infraMuniMap_l <- tm_shape(muni3) +
  tm_borders() +
  tm_shape(infraMuni3) +
  tm_polygons(
    col = "infrastructureIndex",
    style = "cat",
    title = "Human\nImpact\nArea"
  ) +
  tm_layout(legend.only = TRUE,
            legend.position = c("left", "bottom"),
            legend.outside = F)

empty <- tm_shape(muni3) +
  tm_borders(col="white") +
  tm_layout(frame = F)

@@

(methodsMap <- tmap_arrange(
  muniPlot,
  empty,
  infraMuniMap,
  infraMuniMap_l,
  ncol = 2,
  widths = c(.8, .2),
  heights = c(.6, .4),
  outer.margins = NULL
))
